---
title: "Shiny Load Tracker - Template Report"
rmd_output_metadata:
  rsc_email_suppress_scheduled: true
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    orientation: columns
---

```{r preflight_check, results='asis', include=TRUE}
if (
  nchar(Sys.getenv("CONNECT_SERVER")) == 0 ||
  nchar(Sys.getenv("CONNECT_API_KEY")) == 0
) {
  print(htmltools::h4("ERROR: Variables Not Defined"))
  print(htmltools::div(
    "The CONNECT_SERVER and CONNECT_API_KEY",
    "environment variables are required in order for this report",
    "to pull usage data.",
    htmltools::br(),
    htmltools::br(),
    "Please define these variables",
    "and then re-run the report.",
    htmltools::br(),
    htmltools::br(),
    style = "max-width: 600px"
  ))
  knitr::knit_exit("Terminating the report early.")
}
```

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(shiny)
library(lubridate)
library(prettyunits)
library(ggthemes)
source("helpers.R")

app_info <- get_content('046dfd8f-d6c4-4f4d-8097-77f608908a9d')

shiny <- get_shiny_usage(content_guid = '046dfd8f-d6c4-4f4d-8097-77f608908a9d') %>% 
  clean_data() %>%
  mutate(day = round_date(started, "day")) %>%
  filter(day > today() - ddays(2))
data <- list(shiny = shiny)

sf <- stamp("Sunday, Jan 17, 1999")
```

<div class = "row">
<div class = "col-md-5">
#### Application: [`r app_info$title`](`r app_info$url`)
##### Last Published: `r sf(as_date(app_info$last_deployed_time))`
<p>Description: `r app_info$description`</p> 
<p>Access Type: `r app_info$access_type`</p>
</div>

<div class = "col-md-7">
#### Template Directions: 
* Provide an application `GUID`
* Set a tracking window (days or hours)
* Select a "Warning Buffer" based on your total connections allowed: `warn_buffer`
* Set an average "Session Duration" goal - in minutes: `dur_goal`
</div>
</div>

<hr>

Column
-----------------------------------------------------------------------

### Recent Peak Session Load 

```{r}
intervals <- shiny %>%
  mutate(session = interval(started, ended))
totals <- c()
for (i in 1:length(intervals$session)){
  totals <- c(totals, (sum(sapply(intervals$session, function(x) int_overlaps(intervals$session[i,], x)))))
}

load_obs <- max(totals)
max_conns <- app_info$max_processes * app_info$max_conns_per_process
warn_buffer <- max_conns - 5

if (load_obs >= warn_buffer) {
    rmarkdown::output_metadata$set(rsc_email_suppress_scheduled = FALSE)
}

gauge(load_obs, min = 0, max = max_conns, gaugeSectors(
  success = c(0, warn_buffer - 6), warning = c(warn_buffer - 5, warn_buffer - 1), danger = c(warn_buffer, max_conns)
))
```

### Runtime Settings: R Processes Maximum

```{r}
valueBox(
  value = app_info$max_processes,
  icon = "fa-cogs",
  color = "primary"
)
```

### Runtime Settings: Connections per Process

```{r}
valueBox(
  value = app_info$max_conns_per_process,
  icon = "fa-mouse-pointer",
  color = "primary"
)
```

### Average Session Duration (minutes)

```{r}
dur_goal <- 5.5
calc_avg <- mean(shiny$session_duration)/60
avg_dur <- formatC(calc_avg, digits = 1, format = "f")
valueBox(
  value = avg_dur,
  icon = "fa-stopwatch",
  color = if (calc_avg >= dur_goal) "success" else "warning"
)
```


Column {.tabset data-width=900}
-------------------------------------

### Shiny Sessions by Duration

```{r shiny_over_hour}
data$shiny %>%
  mutate(username = join_users(user_guid), username = null_chars(username, "anonymous")) %>%
  {ggplot(transform(., y=order(username, started)),
       aes(x=started, xend=ended, y=y, yend=y, col=username)) +
      ggthemes::theme_fivethirtyeight() +
      xlab("Session Duration") + 
  geom_segment(size=3) +
  scale_y_discrete(breaks=NULL)}
```

### Shiny Sessions by User (Top 5)

```{r shiny_by_user}
data$shiny %>%
    group_by(user_guid) %>% 
    summarise(visits = n()) %>% 
    mutate(username = join_users(user_guid),
           username = null_chars(username, "anonymous")) %>% 
    select(username, visits) %>% 
    arrange(desc(visits)) %>% 
    head(5) %>% 
    {ggplot(., aes(reorder(username, visits), visits)) + 
     geom_bar(stat = "identity") +  
     coord_flip() + 
     labs(
       y = "Number of Shiny Sessions",
       x = NULL
     )}
```

```{r}
library(blastula)
# Link to published banner created in Google Drive
img_link <- "https://docs.google.com/drawings/d/e/2PACX-1vRTgQpvT5VqeQeQsVysPyJnYSZbsLxtYV3etSn0NEk-PxD9_7sljl7JwXI2rar10BakQXkRbSAW-oGv/pub?w=477&h=143"
message <- compose_email(
    body = "
  The runtime settings for: <strong>{app_info$title}</strong> may need to be adjusted.
  
  ![Cute Warning Image]({img_link})
  
  Observed Connections: <strong>{load_obs}</strong> Have recently exceeded the warning buffer of: <strong>{max_conns - warn_buffer}</strong>
  
  Current Runtime Settings:
  
  <ul>
  <li>Max R Processes: {app_info$max_processes}</li> 
  <li>Connections per Process: {app_info$max_conns_per_process}</li>
  </ul>
  
  Access the application here: {app_info$url}
  
  <br />
  Cheers, <br /> 
  Shiny Application Monitoring-Bot"
)
# Set the R Markdown Output Metadata for email body and images
rmarkdown::output_metadata$set(rsc_email_body_html = message$html_str)
rmarkdown::output_metadata$set(rsc_email_subject = sprintf("Runtime Warning: %s", app_info$title))
rmarkdown::output_metadata$set(rsc_email_images = message$images)
```
